Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
shuffle num rep to appendix

\textit{DC Motor Position and Rate} plants describes the angular position and 
velocity of a DC Motor, respectively. 
\textit{Automotive Cruise System} plant represents the speed of a motor vehicle. 
\textit{Helicopter Longitudinal Motion} plant provides the longitudinal motion model 
of a helicopter. 
\textit{Inverted Pendulum} plant describes a pendulum model
with its center of mass above its pivot point. 
\textit{Magnetic Suspension} plant provides a physical model for which 
a given object is suspended via magnetic field. 
\textit{Magnetized Pointer} plant describes a physical model employed in analogue gauges 
and indicators that is rotated through interaction with magnetic fields.
\textit{1/4 Car Suspension} plant presents a physical model that connects a car to its wheels 
and allows relative motion between both parts.
\textit{Computer Tape Driver} plant describes a system to read and write data 
on a storage device in the computer.

Section~\ref{sec:BenchmarksforStateSpace} in the appendix summarizes 
all our benchmarks, which are SISO models (cf. section~\ref{sec:preliminaries}). 
The Inverted Pendulum appears to be a two output system, but it was treated as two 
SISO systems during the experiments. For the sake of simplicity all the states 
measurements are assumed available. In practice, state estimators should be designed 
in order to obtain an estimate of the states from the single output. 
Further work can include 
state observers synthesis.

>>>>

\textit{DC Motor Position and Rate} plants describes the angular position and 
velocity of a DC Motor, respectively. 
\textit{Automotive Cruise System} plant represents the speed of a motor vehicle. 
\textit{Helicopter Longitudinal Motion} plant provides the longitudinal motion model 
of a helicopter. 
\textit{Inverted Pendulum} plant describes a pendulum model
with its center of mass above its pivot point. 
\textit{Magnetic Suspension} plant provides a physical model for which 
a given object is suspended via magnetic field. 
\textit{Magnetized Pointer} plant describes a physical model employed in analogue gauges 
and indicators that is rotated through interaction with magnetic fields.
\textit{1/4 Car Suspension} plant presents a physical model that connects a car to its wheels 
and allows relative motion between both parts.
\textit{Computer Tape Driver} plant describes a physical model to read and write data 
on a storage device in the computer.

Section~\ref{sec:BenchmarksforStateSpace} in the appendix summarizes 
all our benchmarks, which are SISO models (cf. section~\ref{sec:preliminaries}). 
The Inverted Pendulum appears to be a two output system, but it was treated as two 
SISO systems during the experiments. For the sake of simplicity all the states 
measurements are assumed available. In practice, state estimators should be designed 
in order to obtain an estimate of the states from the single output. 
Further extensions of this work can include 
state observers synthesis.
